Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-28 ms.tex
gcm

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{Left: fits to the broadband WFC3 phase curve. Right: best fit temperature maps.}
\label{fig:model_comparison}
\end{figure*}

@@

At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles. We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium.  We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}). Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at dayisde photospheric temperature and pressure (3000 K, 0.1 bar).  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13}, and interpolated in the grid to calculate the likelihood at each model step. We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).

@@

The models with added drag more closely reproduce the small hotspot offset that is observed. The main effect of drag is to slow down advection of heat to the nightside, which shifts the peak brightness closer to the substellar point.  The best fit WFC3 phase curve has a hotspot offset of FIXME. The drag models have offsets of $0.2$ and $2.3$ degrees for $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, compared to $15$ degrees for the nominal GCM.  The drag models also provide a good match to the observed dayside flux, for drag timescales in the range $\tau_\mathrm{drag} = 10^3 - 10^4$ s.  However, the drag models underestimate the flux at longitudes away from the substellar point, predicting a flux FIXME less than what is observed. \textbf{Vivien: are these fast drag timescales even reasonable?}).

Water dissociation!

@@

%\begin{figure}
%	\includegraphics[width = 1.0\textwidth]{WASP-103b-Solar-NoClouds-Photo-abundances-Water-CO-4.5microns-smooth.pdf}
%\caption{Water.}
%\label{fig:dayside}
%\end{figure}

>>>>

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{\textbf{Left:} fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag} = 10^3$ GCM. We also show the planet-to-star flux corresponding to each map (points). The planet-to-star flux is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} temperature maps from the best fit models and the GCM at 0.1 bar.}
\label{fig:model_comparison}
\end{figure*}

@@

At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles. We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium.  We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}). Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at dayside photospheric temperature and pressure (3000 K, 0.1 bar).  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13}, and interpolated in the grid to calculate the likelihood at each model step. We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).

@@

The models with added drag more closely reproduce the small hotspot offset that is observed. The main effect of drag is to slow down advection of heat to the nightside, which shifts the peak brightness closer to the substellar point.  The best fit WFC3 phase curve has a hotspot offset of FIXME. The drag models have offsets of $0.2$ and $2.3$ degrees for $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, compared to $15$ degrees for the nominal GCM.  The drag models also provide a good match to the observed dayside flux, for drag timescales in the range $\tau_\mathrm{drag} = 10^3 - 10^4$ s.  However, the drag models underestimate the flux at longitudes away from the substellar point, predicting 20\% less flux than is observed at quadrature. \textbf{Vivien: are these fast drag timescales even reasonable?}).

We also compared the GCM output to the temperature maps retrieved with \texttt{spiderman}. Figure\,\ref{fig:model_comparison} shows the 0.1 bar temperature map for the $\tau_\mathrm{drag} = 10^3$ GCM compared to the best it models. The GCM has a minimum and maximum temperature of $920$ and $3360$ K, which is most comparable to the fit from the spherical harmonic model.  The GCM nightside temperatures are around $300$ K cooler than the spherical harmonics fit,

. The polar regions are the most discrepant, with temperatures are about $1000$ K cooler in the GCM than the spherical harmonics model.

The GCMs also provide insight into what molecules are present in which parts of the atmosphere. As discussed in \S\,\ref{sec:composition}, water dissociation and H- opacity are needed to explain the dayside emission spectrum. Figure\,\ref{fig:gcmcomposition} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag} = 10^3$ GCM. The water abundance drops by $\sim10$ at the substellar point, and the H- opacity increases by $\sim100$.

\textbf{Vivien: did you run a cloudy model?}

@@

\begin{figure*}
	\includegraphics[width = 1.0\textwidth]{Figures/GCM_abundances.eps}
\caption{Abundances of key molecular species for different viewing geometries, from the $\tau_\mathrm{drag} = 10^3$ GCM.}
\label{fig:GCMabundance}
\end{figure*}
